Verifying a Postfix Language \\ \large CS595 Final Project

### 2021-11-30 project/paper.tex
fix some rules, remove sum types

% Useful packages
\usepackage{amsmath, amsthm, verbatim, enumerate, xcolor, mathpartir}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

% ???
\usepackage{syntax}

@@

\renewcommand{\grammarlabel}[2]{#1 \hfill#2}
\begin{grammar}
    <$\tau$> ::= $\kwInt$
    |    $\kwLong$
    |    $\kwFloat$
    |    $\kwDouble$
    \alt $(\tau^*)$
    |    $\kwUnit$
    |    $\tau_1~ \tau_2~ \texttt{|}$
    |    $\kwArrow{\tau_1} {\tau_2}$
    |    $\kwType{e}$

@@

    <$e^*$> ::= $\varepsilon$ | $e^* ~ e$ | $\kwunpack{e}$
\end{grammar}

Notes
\begin{itemize}
    \item A syntactic fixed point combinator was chosen instead of $\kwrec{\tau^*}{\tau^*}{e^*}$. It's possible that one could be implemented in the language itself.
    \item notice that unpack can have any non-negative number of output values depending on the given input
    \item $\kwunpack{e}$ and $\kwunpack{\tau}$ can give 0 or more outputs depending on the input tuple
\end{itemize}

@@

\subsection{Value Judgements}
{
    \centering
    \def \MathparLineskip {\lineskip=0.43cm}
    \begin{mathpar}

        % fixed point combinator
        \Rule{Fixed Point}{e \val \\ \tau \prim}{\kwfix{e}{\tau} \val}
    \end{mathpar}
}

\subsection{Value and Step Judgement}
Expressions are evaluated from left to right until everything is a value
{
    \centering
    \def \MathparLineskip {\lineskip=0.43cm}
    \begin{mathpar}
        % number literals
        \Rule{V-1}
             {\forall ~ \tau \in \{ \kwInt, \kwLong, \kwFloat, \kwDouble\}}
             {\kwnumlit{n}{\tau} \val}
        \and

        % Tuple literals evaluation
        \Rule{TUPLES-1}
            {e^* \step e^{*\prime}}
            {( e^* ) \step ( e^{*\prime} )}
        \Rule{TUPLES-2}
            {v_i \val ~ \forall v_i \in v^*}
            {(v^*) \val}
        \and

        % Derivation of e* -> e*'
        \Rule{STEP-1}
            {e_1 \step e_1'}
            {e_1 ~ ... ~ e_n \step e_1' ~ ... ~ e_n}
        \and
        \Rule{STEP-2}
            {e_1 \step e_1'
                \\v_i \val ~ \forall~ v_i \in v^*}
            {v^* ~ e_1 ~ ... ~ e_n \step v^* ~ e_1' ~ ... ~ e_n}
        \and
    \end{mathpar}  
}

@@

\subsection{Others}
{
    \centering
    \def \MathparLineskip {\lineskip=0.43cm}
    \begin{mathpar}

@@

        % math
        \Rule{ADD}
            {v_1 \val \\ v_2 \val \\ v_3 = v_1 + v_2}
            {v_1~ v_2~ + \step v_3}
        \Rule{MUL}
            {v_1 \val \\ v_2 \val \\ v_3 = v_1 * v_2}
            {v_1~ v_2~ \times \step v_3}
        \and

        % ternary
        \Rule{TERN-1}
            {v_1 \val \\ v_2 \val}
            {\kwtern{\kwnumlit{0}{\kwInt}}{v_1}{v_2} \step v_2}
        \Rule{TERN-2}
            {v_1 \val \\ v_2 \val \\ n \neq 0}
            {\kwtern{\kwnumlit{n}{\kwInt}}{v_1}{v_2} \step v_1}
        \and
    \end{mathpar}
}

\section{Semantics for Types}
Because there are operations involving types, we have to have a equivalents to $\val$ and $\step$ judgements for types. These are provided by $\prim$ and $\tstep$ respectively with $\prim$ loosely referring to "primitive" types.

\subsection{Primitives}
{
    \centering
    \def \MathparLineskip {\lineskip=0.43cm}
    \begin{mathpar}
        \Rule{P-I32}{\strut}{\kwInt \prim} \and
        \Rule{P-I64}{\strut}{\kwLong \prim} \and
        \Rule{P-F32}{\strut}{\kwFloat \prim} \and
        \Rule{P-F64}{\strut}{\kwDouble \prim} \and
        \Rule{P-sum}{\tau_1 \prim \\ \tau_2 \prim}{\tau_1 \tau_2 \texttt{|} \prim} \and
        \Rule{P-Arrow}{\tau_1 \prim \\ \tau_2 \prim}{\kwArrow{\tau_1}{\tau_2} \prim} \and
    \end{mathpar}  
}

\subsection{Step Judgement and Type operator}
Expressions are evaluated from left to right until everything is a value
{
    \centering
    \def \MathparLineskip {\lineskip=0.43cm}
    \begin{mathpar}
        % Derivation of e* -> e*'
        \Rule{STEP-1}
            {\tau_1 \tstep \tau_1'}
            {\tau_1 ~ ... ~ \tau_n \tstep \tau_1' ~ ... ~ \tau_n}
        \and
        \Rule{STEP-2}
            {\tau_1 \tstep \tau_1'
                \\v_i \prim ~ \forall v_i \in v^*}
            {\tau^* ~ \tau_1 ~ ... ~ \tau_n \tstep v^* ~ \tau_1' ~ ... ~ \tau_n}
        \and

        \Rule{TYPE-1}{v \val \\ \etyped{v}{\tau}}{\kwType{v} \tstep \tau} 
    \end{mathpar}  
}

@@

        \and \Rule{Type-Id}
            {[ ... ~ \kwid{T} \tstep \tau ~ ... ] \in \sigma}
            {\sigma; \kwid{T} \tstep \sigma; \tau}

        \and \Rule{MACRO-1}
            {\tau^* \tstep \tau^{*\prime}}
            {\sigma; \kwmacro{\tau^*}{e^*} \step \sigma; \kwmacro{\tau^{*\prime}}{e^*}}
    \end{mathpar}
}

\subsection{Others}
Notably the step
{
    \centering
    \def \MathparLineskip{\lineskip=0.43cm}
    \begin{mathpar}
        % Tuple type literals evaluation
        \Rule{TTUPLES-1}
            {\tau^* \tstep \tau^{*\prime}}
            {( \tau^* ) \tstep ( \tau^{*\prime} )}
        \Rule{TTUPLES-2}
            {\tau_i \prim ~ \forall \tau_i \in \tau^*}
            {(\tau^*) \prim}
        \and

        % unpack operator
        \Rule{TTUPLES-3}
            {\tau_i \prim ~ \forall~ i \in [1, n]}
            {\kwunpack{(\tau_1 ... \tau_n)} \tstep \tau_1 ... \tau_n}
        \Rule{TTUPLES-4}
            {\strut}
            {\kwunpack{\kwUnit} \tstep \varepsilon}
        \and

        % fixed point combinator
        \Rule{Fixed Point}{e \val \\ \tau \prim}{\kwfix{e}{\tau} \val}
    \end{mathpar}
}

\section{Typing}

\subsection{Step Judgement}
{
    \centering
    \begin{mathpar}
    \Rule{T-0}
        {\typed{\ctx}{e}{\tau} \\ \tau \tstep \tau'}
        {\typed{\ctx}{e}{\tau'}}
    \end{mathpar}
}

\subsection{Math and Logic}
{
    \centering
    \def \MathparLineskip {\lineskip=0.43cm}
    \begin{mathpar}
        \Rule{T-1}{\strut}{\typed{\ctx}{\kwnumlit{n}{\kwInt}}{\kwInt}}
        \and \Rule{T-2}{\strut}{\typed{\ctx}{\kwnumlit{n}{\kwLong}}{\kwLong}}
        \and \Rule{T-3}{\strut}{\typed{\ctx}{\kwnumlit{n}{\kwFloat}}{\kwFloat}}
        \and \Rule{T-4}{\strut}{\typed{\ctx}{\kwnumlit{n}{\kwDouble}}{\kwDouble}}
        \and \Rule{T-5}
            {\typed{\ctx}{e_1}{\tau} 
                \\ \typed{\ctx}{e_2}{\tau} 
                \\ \tau \in \{\kwInt, \kwLong, \kwFloat, \kwDouble\}}
            {\typed{\ctx}{e_1~ e_2~ +}{\tau}}
        \and \Rule{T-6}
            {\typed{\ctx}{e_1}{\tau} 
                \\ \typed{\ctx}{e_2}{\tau} 
                \\ \tau \in \{\kwInt, \kwLong, \kwFloat, \kwDouble\}}
            {\typed{\ctx}{e_1~ e_2~ \times}{\tau}}
        \and \Rule{T-7}
            {\typed{\ctx}{e_1}{\kwInt}
                \\ \typed{\ctx}{e_2}{\tau}
                \\ \typed{\ctx}{e_3}{\tau}}
            {\typed{\ctx}{\kwtern{e_1}{e_2}{e_3}}{\tau}}
    \end{mathpar}
}

@@

        \Rule{Call}
            {\typed{\ctx}{e_1}{\kwArrow{\tau^*}{\tau^{*\prime}}}
                \\ \typed{\ctx}{e^*}{\tau^*}}
            {\typed{\ctx}{e^*~ e_1~ \textbf{@}}{\tau^{*\prime}}}

        \Rule{Identifier}
            {\ctx(\kwid{x}) = \tau}
            {\typed{\ctx}{\kwid{x}}{\tau}}

\section{Proofs}
\subsection{Theorem - Progress}
If $\etyped{e^*}{\tau^*}$ then either $e^*\step e^{*\prime}$ or $e_i \val~ \forall~ e_i \in e^*$.
\begin{proof}
    By induction on the derivation of $\etyped{e^*}{\tau^*}$.
    \begin{itemize}
        \item (T-\{1,2,3,4\})
            Then $e^* = e = \kwnumlit{n}{\tau}$, where $\tau \in \{ \kwInt, \kwLong, \kwFloat, \kwDouble \}$.
            By (V-1), $\kwnumlit{n}{\tau} \val$, so $e^* \val$.

        \item (T-5)
            Then $e^* = e = e_1~ e_2~ +$ and $\kwtyped{e_1}{\tau}$ and $\kwtyped{e_2}{\tau}$ for some $\tau \in \{ \kwInt, \kwLong, \kwFloat, \kwDouble \}$.

            By induction, $e_1 \step e_1'$ or $e_1 val$.
            If $e_1 \step e_1'$, then by \Rulename{STEP-1}, $e \step e_1'~ e_2~ +$.

            If $e_1 \val$, then by induction, $e_2 \step e_2'$ or $e_2 val$.
            If $e_1 \val$ and $e_2 \step e_2'$, then by \Rulename{STEP-2}, $e \step e_1~ e_2'~ +$.

            If $e_1 \val$ and $e_2 \val$, then $e_1 = \kwnumlit{n_1}{\tau}, e_2 = \kwnumlit{n_2}{\tau}$, and by \Rulename{ADD}, $e+ \step \kwnumlit{n_1 + n_2}{\tau}$.
    \end{itemize}
\end{proof}

>>>>

% Useful packages
\usepackage{amsmath, amsthm, verbatim, enumerate, xcolor, mathpartir}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{syntax}

@@

\renewcommand{\grammarlabel}[2]{#1 \hfill#2}
\begin{grammar}
    <$\tau$> ::= $\kwInt$
    |    $\kwLong$
    |    $\kwFloat$
    |    $\kwDouble$
    \alt $(\tau^*)$
    |    $\kwUnit$
    % |    $\tau_1~ \tau_2~ \texttt{|}$
    |    $\kwArrow{\tau_1} {\tau_2}$
    |    $\kwType{e}$

@@

    <$e^*$> ::= $\varepsilon$ | $e^* ~ e$ | $\kwunpack{e}$
\end{grammar}
Notes
\begin{itemize}
    \item A syntactic fixed point combinator was chosen instead of $\kwrec{\tau^*}{\tau^*}{e^*}$. It's possible that one could be implemented in the language itself.
    \item Tuples and Tuple types are enclosed in parens
    \item $\kwunpack{e}$ and $\kwunpack{\tau}$ can give 0 or more outputs depending on the input tuple
\end{itemize}

@@

\subsection{Value and Step Judgement}
The step judgement states that expressions are evaluated from left to right until everything is a value. Values are defined further as we go through.
{
    \centering
    \def \MathparLineskip {\lineskip=0.43cm}
    \begin{mathpar}
        % Derivation of e* -> e*'
        \Rule{STEP}
            {e_1 \step e_1'
                \\v_i \val ~ \forall~ v_i \in v^*}
            {v^* ~ e_1 ~ ... ~ e_n \step v^* ~ e_1' ~ ... ~ e_n}
        \and

        % number literals
        \Rule{V-1}
             {\forall ~ \tau \in \{ \kwInt, \kwLong, \kwFloat, \kwDouble\}}
             {\kwnumlit{n}{\tau} \val}
        \and

        % Tuple literals evaluation
        \Rule{TUPLES-1}
            {e^* \step e^{*\prime}}
            {( e^* ) \step ( e^{*\prime} )}
        \Rule{TUPLES-2}
            {v_i \val ~ \forall v_i \in v^*}
            {(v^*) \val}
        \and
    \end{mathpar}  
}

@@

\subsection{Others}
Notice the use of the \href{https://en.wikipedia.org/wiki/Kronecker_delta}{Kronecker Delta} to define the equals operator.
{
    \centering
    \def \MathparLineskip {\lineskip=0.43cm}
    \begin{mathpar}

@@

        % math
        \Rule{ADD}
            {v_1 \val \\ v_2 \val \\ v_3 = v_1 + v_2}
            {v_1~ v_2~ + \step v_3}
        \and
        \Rule{MUL}
            {v_1 \val \\ v_2 \val \\ v_3 = v_1 * v_2}
            {v_1~ v_2~ \times \step v_3}
        \and

        % Comparisons
        \Rule{EQUIV}
            {v_1 \val \\ v_2 \val}
            {v_1~ v_2~ ==~ \step \kwnumlit{(\delta_{v_1 v_2})}{\kwInt}}

        % Ternary
        \Rule{TERN-1}
            {v_1 \val \\ v_2 \val}
            {\kwtern{\kwnumlit{0}{\kwInt}}{v_1}{v_2} \step v_2}
        \Rule{TERN-2}
            {v_1 \val \\ v_2 \val \\ n \neq 0}
            {\kwtern{\kwnumlit{n}{\kwInt}}{v_1}{v_2} \step v_1}
        \and
    \end{mathpar}
}

\section{Semantics for Types}
Because there are operations involving types, we have to have a equivalents to $\val$ and $\step$ judgements for types. These are provided by $\prim$ and $\tstep$ respectively.

\subsection{Primitives}
{
    \centering
    \def \MathparLineskip {\lineskip=0.43cm}
    \begin{mathpar}
        \Rule{P-I32}{\strut}{\kwInt \prim} \and
        \Rule{P-I64}{\strut}{\kwLong \prim} \and
        \Rule{P-F32}{\strut}{\kwFloat \prim} \and
        \Rule{P-F64}{\strut}{\kwDouble \prim} \and
        %\Rule{P-sum}{\tau_1 \prim \\ \tau_2 \prim}{\tau_1 \tau_2 \texttt{|} \prim} \and
        \Rule{P-Arrow}{\tau_1 \prim \\ \tau_2 \prim}{\kwArrow{\tau_1}{\tau_2} \prim} \and
    \end{mathpar}  
}

\subsection{Step Judgement}
Type expressions are evaluated left to right until everything is $\prim$.
{
    \centering
    \def \MathparLineskip {\lineskip=0.43cm}
    \begin{mathpar}
        % Derivation of T* -> T*'
        \Rule{TSTEP}
            {\tau_1 \tstep \tau_1'
                \\\tau_i \prim ~ \forall \tau_i \in \tau^*}
            {\tau^* ~ \tau_1 ~ ... ~ \tau_n \tstep \tau^* ~ \tau_1' ~ ... ~ \tau_n}
        \and
    \end{mathpar}  
}

@@

        \and \Rule{Type-Id}
            {[ ... ~ \kwid{T} \tstep \tau ~ ... ] \in \sigma}
            {\sigma; \kwid{T} \tstep \sigma; \tau}
    \end{mathpar}
}

\subsection{Tuples}
{
    \centering
    \def \MathparLineskip{\lineskip=0.43cm}
    \begin{mathpar}
        % Tuple type literals evaluation
        \Rule{Tuple Types - 1}
            {\tau^* \tstep \tau^{*\prime}}
            {( \tau^* ) \tstep ( \tau^{*\prime} )}
        \Rule{Tuple Types - 2}
            {\tau_i \prim ~ \forall \tau_i \in \tau^*}
            {(\tau^*) \prim}
        \and

        % unpack operator
        \Rule{Tuple Types - 3}
            {\tau_i \prim ~ \forall~ i \in [1, n]}
            {\kwunpack{(\tau_1 ... \tau_n)} \tstep \tau_1 ... \tau_n}
        \Rule{Tuple Types - 4}
            {\strut}
            {\kwunpack{\kwUnit} \tstep \varepsilon}
        \and
    \end{mathpar}
}

\subsection{Others}
{
    \centering
    \def \MathparLineskip{\lineskip=0.43cm}
    \begin{mathpar}
        \Rule{Type Equiv}
            {\tau_1 \prim \\ \tau_2 \prim}
            {\tau_1~ \tau_2~ ==~ \tstep~ \kwnumlit{(\delta_{\tau_1 \tau_2})}{\kwInt}}

        % fixed point combinator
        \and \Rule{Fixed Point}{e \val \\ \tau \prim}{\kwfix{e}{\tau} \val}

        % input types for macros can step
        \and \Rule{Macro Type Step}
            {\tau^* \tstep \tau^{*\prime}}
            {\sigma; \kwmacro{\tau^*}{e^*} \step \sigma; \kwmacro{\tau^{*\prime}}{e^*}}

        % typeof operator
        \Rule{TYPE-1}{v \val \\ \etyped{v}{\tau}}{\kwType{v} \tstep \tau} 
    \end{mathpar}
}

\section{Typing}
Note that because our notation is defined as ignoring irrelevant values there could be  
\subsection{Step Judgement}
{
    \centering
    \begin{mathpar}
    \Rule{T-0}
        {\typed{\ctx}{e}{\tau} \\ \tau \tstep \tau'}
        {\typed{\ctx}{e}{\tau'}}
    \end{mathpar}
}

\subsection{Math and Logic}
{
    \centering
    \def \MathparLineskip {\lineskip=0.43cm}
    \begin{mathpar}
        \Rule{T-1}{\strut}{\typed{\ctx}{\kwnumlit{n}{\kwInt}}{\kwInt}}
        \and \Rule{T-2}{\strut}{\typed{\ctx}{\kwnumlit{n}{\kwLong}}{\kwLong}}
        \and \Rule{T-3}{\strut}{\typed{\ctx}{\kwnumlit{n}{\kwFloat}}{\kwFloat}}
        \and \Rule{T-4}{\strut}{\typed{\ctx}{\kwnumlit{n}{\kwDouble}}{\kwDouble}}
        \and \Rule{T-5}
            {\typed{\ctx}{e_1}{\tau} 
                \\ \typed{\ctx}{e_2}{\tau} 
                \\ \tau \in \{\kwInt, \kwLong, \kwFloat, \kwDouble\}}
            {\typed{\ctx}{e_1~ e_2~ +}{\tau}}
        \and \Rule{T-6}
            {\typed{\ctx}{e_1}{\tau} 
                \\ \typed{\ctx}{e_2}{\tau} 
                \\ \tau \in \{\kwInt, \kwLong, \kwFloat, \kwDouble\}}
            {\typed{\ctx}{e_1~ e_2~ \times}{\tau}}
        \and \Rule{T-7}
            {\typed{\ctx}{e_1}{\kwInt}
                \\ \typed{\ctx}{e_2}{\tau}
                \\ \typed{\ctx}{e_3}{\tau}}
            {\typed{\ctx}{\kwtern{e_1}{e_2}{e_3}}{\tau}}
        \and \Rule{T-8}
            {\typed{\ctx}{e_1}{\tau}
                \\ \typed{\ctx}{e_2}{\tau}
                \\ \tau \in \{ \kwInt, \kwLong, \kwFloat, \kwDouble \}}
            {\typed{\ctx}{e_1~ e_2~ ==~}{\kwInt}}
        \and \Rule{T-9}
            {\tau_1 \prim
                \\ \tau_2 \prim}
            {\typed{\ctx}{\tau_1~ \tau_2~ ==~}{\kwInt}}
    \end{mathpar}
}

@@

        \and \Rule{Call}
            {\typed{\ctx}{e_1}{\kwArrow{\tau^*}{\tau^{*\prime}}}
                \\ \typed{\ctx}{e^*}{\tau^*}}
            {\typed{\ctx}{e^*~ e_1~ \textbf{@}}{\tau^{*\prime}}}

        \and \Rule{Identifier}
            {\ctx(\kwid{x}) = \tau}
            {\typed{\ctx}{\kwid{x}}{\tau}}
        \and \Rule{Let}
            {\typed{\ctx}{e}{\tau}
                \\ \ctx(\kwid{x}) = e}
            {\typed{\ctx}{e \kwid{x}}{\varepsilon}}

        \and \Rule{Fix}
            {\tau_1 \prim
                \\ \typed{\ctx}{e}{\tau_2}
                \\ \tau_2 \prim
                \\ \tau_2 = \kwArrow{\tau^*_3 ~ \kwArrow{\tau^*_3}{\tau^*_4}}{\tau^*_4}}
            {\typed{\ctx}{\kwfix{e}{\tau_1}}{\kwArrow{\tau^*_3}{\tau^*_4}}}
    \end{mathpar}
}

\section{Proofs}
\subsection{Theorem - Progress}
If $\etyped{e^*}{\tau^*}$ then either $e^*\step e^{*\prime}$ or $e_i \val~ \forall~ e_i \in e^*$.
\begin{proof}
    By induction on the derivation of $\etyped{e^*}{\tau^*}$.
    \begin{itemize}
        \item (T-\{1,2,3,4\})
            Then $e^* = \kwnumlit{n}{\tau}$, where $\tau \in \{\kwInt, \kwLong, \kwFloat, \kwDouble\}$.
            By (V-1), $\kwnumlit{n}{\tau} \val$, so $e^* \val$.

        \item (T-5)
            Then $e^* = e_1~ e_2~ +$ and $\etyped{e_1}{\tau}$ and $\etyped{e_2}{\tau}$ for some $\tau \in \{\kwInt, \kwLong, \kwFloat, \kwDouble\}$.

            By induction, $e_1 \step e_1'$ or $e_1 \val$.
            If $e_1 \step e_1'$, then by \Rulename{STEP-1}, $e^* \step e_1'~ e_2~ +$.

            If $e_1 \val$, then by induction, $e_2 \step e_2'$ or $e_2 \val$.
            If $e_1 \val$ and $e_2 \step e_2'$, then by \Rulename{STEP-2}, $e^* \step e_1~ e_2'~ +$.

            If $e_1 \val$ and $e_2 \val$, then by CF, $e_1 = \kwnumlit{n_1}{\tau}, e_2 = \kwnumlit{n_2}{\tau}$, and by \Rulename{ADD}, $e^* \step \kwnumlit{n_1 + n_2}{\tau}$.

        \item (T-6)
            $[\times / +][\Rulename{MUL} / \Rulename{ADD}]$ (T-5)

        \item (T-7)
            Then $e^* = \kwtern{e_1}{e_2}{e_3}$ and $\etyped{e_1}{\kwInt}$. %and $\etyped{e_2}{\tau}$ and $\etyped{e_3}{\tau}$ for some $\tau$.

            By induction, $e_1 \step e_1'$ or $e_1 \val$.
            If $e_1 \step e_1'$, then by \Rulename{STEP-1}, $e^* \step \kwtern{e_1'}{e_2}{e_3}$.

            If $e_1 \val$, then by induction, $e_2 \step e_2'$ or $e_2 \val$.
            If $e_1 \val$ and $e_2 \step e_2'$, then by \Rulename{STEP-2}, $e^* \step \kwtern{e_1}{e_2'}{e_3}$.

            If $e_1 \val$ and $e_2 \val$, then by induction, $e_3 \step e_3'$ or $e_3 \val$.
            If $e_1 \val$ and $e_2 \val$ and $e_3 \step e_3'$, then by \Rulename{STEP-2}, $e \step \kwtern{e_1}{e_2}{e_3'}$.

            If $e_1 \val$ and $e_2 \val$ and $e_3 \val$, then by CF, $e_1 = \kwnumlit{n}{\kwInt}$.

            If $n = 0$, then by \Rulename{TERN-1}, $e^* \step e_3$.
            Otherwise, $n \neq 0$, so by \Rulename{TERN-2}, $e^* \step e_2$.

        \item \Rulename{Empty Tuple}
            Then $e^* = ()$. By \Rulename{TUPLES-2}, $() \val$.

        \item \Rulename{Tuple Type}
            Then $e^* = (e^*_t) = (e_1~ e_2~ ...~ e_n)$.

            By induction, $\forall e_i \in e^*_t$, $e_i \val$ or $e_i \step e_i'$.

            % Then either all elements are values or there exists some *first* steppable element
            % if there's a steppable element, then e^*_t steps using STEP-{1,2}, so e^* steps using TUPLES-1
            % if there are no steppable elements, then all elements are values, so e^* \val by TUPLES-2
    \end{itemize}
\end{proof}
